\documentclass[a4paper,10pt]{article}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage[latin1]{inputenc}
\usepackage{cite}
\usepackage[table]{xcolor}
\usepackage{newclude}
\usepackage{hyperref}
\usepackage{indentfirst}
\usepackage[super]{nth}

\begin{document}

    \title{MineSweeper 3D}

    \author{Isaiah Martinez \\ CSUN \\ Computer Science Department \\ isaiah.martinez.891@my.csun.edu}
          
    \date{03/08/2024}

    \maketitle
   
    \tableofcontents

    \newpage

    \section{Change History}

    Version: 0.09

    Modifier: Isaiah Martinez
    
    Date: 2/19/24
    
    Description of Change: Discussed High Level Architecture of the project: Unity for modeling, C\#/Python for helper script, Python for ML training, and JS for API connectivity.
    Added template to follow for documentation.
    Structured git repo directories.
    First, we will be working on a set amount of locations with small amount of available traffic data.
    Later, we hope to implement API connectivity to obtain traffic info and map data with more locations.
 
    %horizontal line
    \noindent\rule{12cm}{0.4pt}

    Version: 0.05

    Modifier: Isaiah Martinez
    
    Date: 2/12/24
    
    Description of Change: Made Git repository. 
    Looked at scholarly articles for related works.
    Uploaded sample scholarly article to view.
    Laid out big ideas for project.
    Began work on models to be used in Unity.
 
    \include*{Intro}
    \newpage
    \include*{DesignGoals}
    \include*{SysBehavior}
    \include*{LogView}
    \include*{ProcessView}
    \include*{DevView}
    \include*{PhysView}
    \include*{UCView}
    \include*{Reflection}
    \include*{Acknowledgements}

\end{document}